Opening up the court (surface) in tennis grand slams

### 2019-08-21 contest/graphics/graphics_for_paper.Rmd
update code for p-values for chi squared tests spainiards

with(filter(gs_players, ioc == "ESP", round == "R128"),
     table(did_win, tournament)) %>%
  chisq.test(correct = TRUE)

@@

>>>>

################################################################################
# TESTS FOR PAPER
################################################################################
with(filter(gs_players, ioc == "ESP", round == "R128"),
     table(did_win, tournament)) %>%
  chisq.test(correct = TRUE)
with(filter(gs_players, ioc == "ESP", round == "R64"),
     table(did_win, tournament)) %>%
  chisq.test(correct = TRUE)
with(filter(gs_players, ioc == "ESP", round == "R32"),
     table(did_win, tournament)) %>%
  chisq.test(correct = TRUE)
with(filter(gs_players, ioc == "ESP", round == "R16"),
     table(did_win, tournament)) %>%
  chisq.test(correct = TRUE)
```

@@

p_atp_percent <- gs_players %>% filter(league == "ATP") %>%
ggplot( aes(log(ht+1), ace/svpt)) + 
  geom_jitter(aes(color = tournament), size=1.5) + 
  # scale_color_manual(" ", values = tournament_colors) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=atp_servers,
            aes(log(ht+1), ace/svpt, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 7) + 
  geom_label_repel(data=atp_servers,
            aes(log(ht+1), ace/svpt, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 7) +
  labs(x = "log(height + 1)", y = "ace% = aces / serves", title = "ATP") +
  my_theme + scale_color_manual("Tournament",
                                values = tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)\n",
                                           "French Open\n(Clay)\n",
                                           "US Open\n(DecoTurf)\n",
                                           "Wimbledon\n(Grass)\n")) +
  guides(color = guide_legend(override.aes = list(size = 7, shape=15)))

p_wta_percent <- gs_players %>% filter(league == "WTA") %>%
ggplot(aes(log(ht+1), ace/svpt)) + 
  geom_jitter(aes(color = tournament)) + 
  # scale_color_manual(" ", values = tournament_colors) + 
  geom_smooth(method = "lm", color="black") + 
  geom_label_repel(data=wta_servers,
            aes(log(ht+1), ace/svpt, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 7) + 
  geom_label_repel(data=wta_servers,
            aes( log(ht+1), ace/svpt, label=name),
            seed=1234, fill=NA, show.legend=FALSE, size = 7) +
  labs(x = "log(height + 1)", y = "ace%  = aces / serves", title = "WTA")+
  my_theme + scale_color_manual("Tournament",
                                values = tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)\n",
                                           "French Open\n(Clay)\n",
                                           "US Open\n(DecoTurf)\n",
                                           "Wimbledon\n(Grass)\n")) +
  guides(color = guide_legend(override.aes = list(size = 7, shape=15)))

ggarrange(p_atp_percent, p_wta_percent, common.legend = TRUE, legend="bottom") 
# %>%  grid.arrange(top = textGrob("Taller players are better servers: confirmed",
#                             gp=gpar(fontsize=20, fontfamily="serif")))

# ggsave("plots/aces.jpg", height=7, width=16)
ggsave("plots/aces2_percent.jpg", height=8, width=graphic_width_long)
